---
title: "Question 1"
output: html_document
---

```{r}
library(httr)
library(tidyverse)
library(jsonlite)
```


[Quote Graden](https://github.com/pprathameshmore/QuoteGarden) is an API for about quotes. The website says that it has more than 5000 quotes.

By using that API, do the followings


##### (a) Get a random quote.
```{r}
fromJSON("https://quote-garden.herokuapp.com/api/v2/quotes/random")$quote$quoteText
```


##### (b) Get all quotes by Albert Einstein. There are how many of them? 
(Do not double count identital quotes).

PS 1: there are actually quotes differ only by punctuations, treat them as different quotes for simplicity.
PS 2: you will need to use `URLencode` to quote any names with spaces.

```{r}
library(tidyverse)
lst <- list()
i <- 1
repeat{
    url <- str_glue("https://quote-garden.herokuapp.com/api/v2/authors/{author}?page={page}&limit=200", 
                    author="Albert Einstein", page=i)
    url <- URLencode(url)
    dat <- fromJSON(url)
    if(length(dat$quotes)==0){
      break
    }else{
      lst[[i]] <- dat$quotes
    }
    i <- i + 1
}
```

```{r}
quotes <- do.call("rbind", lst)
quotes <- quotes[!duplicated(quotes$quoteText),]
rmarkdown::paged_table(quotes)
nrow(quotes)
```



##### (c) Get a random quote in a genre "education".

Hint: The API does not directly support it, work around it by using loop.
```{r}
quote <- ""
repeat{
    dat <- fromJSON("https://quote-garden.herokuapp.com/api/v2/quotes/random")
    if(!is.null(dat$quote$quoteGenre)){
      if(dat$quote$quoteGenre=="education"){
        quote <- dat$quote$quoteText
        break
      }
    }
}
quote
```



##### (d) Who said the following quote?

> When performance exceeds ambition, the overlap is called success.

Hint: the endpoint for searching quotes in missing from the website, but it is on the github repo.

```{r}
url <- str_glue("https://quote-garden.herokuapp.com/api/v2/quotes/{query}?page=1&limit=1", query="When performance exceeds ambition, the overlap is called success.")
url <- URLencode(url)
dat <- fromJSON(url)
dat$quotes$quoteAuthor
```
