---
title: "Question 2"
output: 
  html_document: 
    df_print: default
---

In this question, you will be asked to use Yelp API to perform some tasks.

First, you will need to register an app on Yelp platform: https://www.yelp.com/developers/v3/manage_app

Copy the API key in the file `.Renviron` and do not push it to github!
```{r, eval = FALSE}
usethis::edit_r_environ("project")
```


```{r, eval = FALSE}
readRenviron(".Renviron")
```

##### (a) Use the "search" endpoint to search for Davis's "Burgers and Brew" and get its `id`.
```{r warning=F, message=F}
library(jsonlite)
library(tidyverse)
library(httr)

r <- GET(
  "https://api.yelp.com/v3/businesses/search",
  query = list(
    term="Burgers and Brew",
    location="403 3rd St Davis, CA 95616",
    limit=1
  ),
  add_headers(Authorization = paste("Bearer", Sys.getenv("KEY")))
)
stop_for_status(r)
json <- content(r, as = "text")
dat <- fromJSON(json)
bzId <- dat$businesses$id
bzId
```


##### (b) Use the "detail" endpoint to fetch "Burgers and Brew"'s business hour.
```{r}
r <- GET(
  str_glue("https://api.yelp.com/v3/businesses/{id}", id=bzId),
  add_headers(Authorization = paste("Bearer", Sys.getenv("KEY")))
)
json <- content(r, as = "text", encoding = "UTF-8")
dat <- fromJSON(json)
dat$hours$open
```


##### (c) By using the reviews endpoint, get some reviews for "Burgers and Brew".

PS: there is a hard limitation that only 3 reviews are returned. 

```{r}
r <- GET(
  str_glue("https://api.yelp.com/v3/businesses/{id}/reviews", id=bzId),
  add_headers(Authorization = paste("Bearer", Sys.getenv("KEY")))
)
json <- content(r, as = "text", encoding = "UTF-8")
dat <- fromJSON(json)
rmarkdown::paged_table(dat$reviews)
```


##### (d) It is possible to use webscrapping to get more reviews from yelp website directly https://www.yelp.com/biz/burgers-and-brew-davis. Try to get 40 reviews (user, date, rating and review content) from it. 

PS: you only need static web scrapping.
Remark: Do q3 first before attemping this question. It is not easy because yelp is avoiding user to "inpect" the source code.

```{r warning=T}
library(rvest)

nodes <- read_html("https://www.yelp.com/biz/burgers-and-brew-davis") %>% html_nodes("script") 
reviews <- nodes[10] %>% html_text() %>% fromJSON()
dat1 <- as.matrix(reviews$review)

nodes <- read_html("https://www.yelp.com/biz/burgers-and-brew-davis?start=20") %>% html_nodes("script") 
reviews <- nodes[10] %>% html_text() %>% fromJSON()
dat2 <- as.matrix(reviews$review)
dat<- rbind(dat1, dat2)
dat <- as.data.frame(dat)
row.names(dat) <- NULL
dat <- dat %>% select(author,everything())
rmarkdown::paged_table(dat)
```