---
title: "Question 1"
output: html_document
---

```{r}
library(tidyverse)
```

It is an chance for you to practice your skills on regular expressions.


(a) Consider the `phones.txt` files, extract all the telephone/fax numbers and format them as `(xxx)-xxx-xxxx`. (Hint: there should be 24 of them.)

```{r}
read_file("phones.txt") %>%
    str_extract_all("\\(?\\d{3}\\)?[ -/\\.]?\\d{3}[ -\\.]\\d{4}") %>% 
    unlist() %>%
    str_remove("\\(") %>%
    str_remove("\\)") %>% 
    str_replace_all("/", "-") %>%
    str_replace_all(" ", "-") %>%
    str_replace_all("\\.", "-") %>%
    str_replace_all("(\\d{3})(.*)", "(\\1)\\2")
```


(b) Given the two vectors,

```{r}
strings <- c(
    "http://www.foufos.gr",
    "https://www.foufos.gr",
    "http://foufos.gr",
    "http://www.foufos.gr/kino",
    "http://werer.gr",
    "www.foufos.gr",
    "www.mp3.com",
    "www.t.co",
    "http://t.co",
    "http://www.t.co",
    "https://www.t.co",
    "www.aa.com",
    "http://aa.com",
    "http://www.aa.com",
    "https://www.aa.com",
    "https://www.aa.com"
)
strings2 <- c(
    "www.foufos",
    "www.foufos-.gr",
    "www.-foufos.gr",
    "foufos.gr",
    "http://www.foufos",
    "http://foufos",
    "www.mp3#.com"
)
```

Write a regular expression `regex` that will match all of `strings` and non of the `strings2`.

```{r}
regex <- "(^www\\.\\w+\\.\\w+$)|(^https?://(www\\.)?\\w+\\.\\w{1,3}(/\\w+)?$)"
all(str_detect(strings, regex))
all(str_detect(strings2, regex, negate = TRUE))
```



(c) Write a regular expression that matches the answers to the question

> What are the colours of the French flag (in any order)?

```{r}
answers <- c(
   "blue, white, red",
   "blue, white and red",
   "blue, red, white",
   "blue, red and white",
   "white, red, blue",
   "white, red and blue",
   "white, blue, red",
   "white, blue and red",
   "red, blue, white",
   "red, blue and white",
   "red, white, blue",
   "red, white and blue"
)
regex <- "(^blue, white(, )|( and )red$)|(^blue, red(, )|( and )white$)|(^white, red(, )|( and )blue$)|(^white, blue(, )|( and )red$)|(^red, blue(, )|( and )white$)|(^red, white(, )|( and )blue$)"
all(str_detect(answers, regex))
```
