---
title: "q2.Rmd"
output: html_document
---

```{r}
library(tidyverse)
library(tidytext)
```

```{r}
simpsons <- read_csv("simpsons_dataset.csv")
```

This dataset contains a number of scripts played by different Simpson characters. We hope to learn some similarity and differences between different characters.

###### (a) Discard the characters which have less than 50 scripts (rows). Use the same dataset for the following questions.

```{r}
df <- simpsons %>% group_by(role) %>% summarise(count=n()) %>% arrange(desc(count)) %>% 
  na.omit() %>% filter(count>=50)
simpsons <- simpsons %>% filter(role %in% df$role)
```



###### (b) What's Homer Simpson most spoken non stop word?
```{r}
simpson_tokens <- simpsons %>% 
  unnest_tokens(word, spoken_words) %>% 
  anti_join(stop_words)

simpson_tokens %>% filter(role=="Homer Simpson") %>%  group_by(word) %>% 
  summarise(count=n()) %>% arrange(desc(count)) %>% na.omit() %>%  head(1)
```





###### (c) By using bigrams, what is the most spoken two-word pharse spoken by Homer?

Hint: remember to remove stop words.

```{r}
df <- simpsons %>% filter(role=="Homer Simpson")
tibble(id=1:nrow(df), text=df$spoken_words) %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  anti_join(stop_words, by=c("word1"="word")) %>% 
  anti_join(stop_words, by=c("word2"="word")) %>% 
  na.omit() %>%
  unite(bigram, word1:word2, sep = " ") %>%
  group_by(bigram) %>% summarise(count=n()) %>%
  arrange(desc(count)) %>%
  head(1)
```



###### (d) What's the most significant word spoken by Homer in terms of `tf-idf`?
```{r}
simpsons %>% unnest_tokens(word, spoken_words) %>% anti_join(stop_words) %>% group_by(word, role) %>%      summarise(n=n()) %>%
  bind_tf_idf(word, role, n) %>% 
  filter(role=="Homer Simpson") %>%
  arrange(desc(tf_idf)) %>%
  select(word, role, n, tf_idf) %>%
  head(1)
```






###### (e) Use hierarchical clustering to classify the characters with Family name "Simpson".
```{r}
library(proxy)
tokens <- simpsons %>% filter(grepl("Simpson", role)) %>%
  unnest_tokens(word, spoken_words) %>% 
  anti_join(stop_words) %>% group_by(role, word) %>% summarise(n=n())
docsdissim <- dist(as.matrix(cast_dtm(tokens, role, word, n)), method = "cosine")
h <- hclust(docsdissim, method = "ward.D2")
plot(h)
```
