---
title: "Question 2"
---

Consider the `flights` dataset in the package `nycflights13`.

```{r, message = FALSE}
library(nycflights13)
library(tidyverse)
```


##### (a) Add a column that is the amount of time gained in the air (`gain = dep_delay - arr_delay`)
```{r}
flights <-  flights %>% mutate(gain=dep_delay-arr_delay)

```
### gain is added on last column


##### (b) Sort part (a) descedingly by the column you just created. Store the result as `flights_gain`.
```{r}
flights_gain <- flights %>% arrange(desc(gain))

```


##### (c) On average, did flights gain or lose time? (Hint: not average gain, but as percentage of positive gain.)
```{r}
  
mean(flights_gain$gain>0, na.rm=T)
```


##### (d) On average, did flights heading to SeaTac ("SEA") gain or loose time?
```{r}

mean(flights_gain$gain[flights_gain$dest=="SEA"]>0, na.rm=T)

```

Gain time

##### (e) Summerize the mean, min and max of the `air_time` column for flights from `JFK` to `SEA`.
```{r}
flights_gain %>% filter(origin=="JFK" & dest=="SEA") %>% 
  summarise(
    mean=mean(air_time, na.rm=T), 
    min=min(air_time, na.rm=T), 
    max=max(air_time, na.rm=T)
  )


```


##### (f) In which month was the average departure delay the greatest?
```{r}
flights_gain %>% group_by(month) %>% summarise(avg=mean(dep_delay, na.rm=T)) %>% 
  arrange(desc(avg))
```
July


##### (g) In which airport were the average arrival delays the highest?
```{r}

flights_gain %>% group_by(dest) %>% summarise(avg=mean(arr_delay, na.rm=T)) %>% 
  arrange(desc(avg)) %>% head(1)

```

CAE 

#####  (h) Which city was flown to with the highest average speed?
```{r}
flights_gain %>% group_by(dest) %>% mutate(speed=distance/air_time) %>% summarise(avg=mean(speed, na.rm=T)) %>% 
  arrange(desc(avg)) %>% head(1)


```
ANC

##### (i) Create a data frame of the average arrival delay for each destination, then use` left_join` to join on the `airports` dataframe, which has the airport info. (Hint: read the documentation of `airports` for the airport codes.)

```{r}
flights_gain %>% group_by(dest) %>%  summarise(avg_delay=mean(arr_delay, na.rm=T)) %>% 
  left_join(airports, by=c("dest"="faa"))

```

