---
title: "Question 3"
---

##### (a) There is a csv file called `groceries.csv` in this directory. Read the csv file using `read_csv` from `tidyverse` and store the data frame as `groceries`. The datset shows the prices of some common groceries item in 4 different stores.The table shows the prices of different items in 4 different stores.
```{r  message = FALSE}
library(readr)
groceries=read_csv("groceries.csv")

```



##### (b) Is the data frame in wide format or long format?

#Answer the data frame is in wide format


##### (c) Try to convert it into the other format. Store it as `groceries2`.
```{r}
library(tidyverse)
groceries2=groceries %>% pivot_longer(-groceries,names_to = "store",names_prefix = "store",values_to = "price")
```
##### (d) Use a randomized block design to analysis the store prices. Is there a store marking up the item prices?
```{r}
fit.lm=lm(price~store+groceries,data = groceries2)
anova(fit.lm)


```

#Answer(d) Since the p-value for store is 0.01273, there is a store marking up the item prices.